---
title: "Developing Data Products - Plot using Plotly"
author: "Vasuprad Kanade"
date: "October 13, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
##Vasuprad.Kanade@accenture.com
## Course 9-Developing Data Products - Assignment 2
```

### Introduction

Course 9 - Developing Data Products - Week 2 - Assignment 1: Create a web page using R Markdown that features a map created with Leaflet.

The goal of the project is to create a web page presentation using R Markdown that features a plot created with Plotly, and to host the resulting web page on either GitHub Pages, RPubs, or NeoCities.


```{r Initiation}
library(ggplot2)
library(plotly)
```

### Plot IRIS flower data using Plotly 
This segment of code selects the relevant data columns, aggregates property damage and crop damage. USe the Damage EXP tp compute total damages.

```{r Data Processing IRIS, echo=TRUE}
filename <- "iris.csv"

# Load the CSV file from the local directory
dataset <- read.csv(filename, header=FALSE)

# Set the column names in the dataset
colnames(dataset) <- c("Sepal.Length","Sepal.Width","Petal.Length","Petal.Width","Species")
head(dataset)

```

### Plot using Plotly
Using ColorBrewer Palette Names
```{r}
# plot data
p <- plot_ly(data = iris, x = ~Sepal.Length, y = ~Petal.Length, color = ~Species, colors = "Set1")

p

```

